Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Remove variance phrase & comment

As shown in Figure \ref{fig:folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only is the average accuracy improved, but the variance between fold-wise accuracies is also reduced, such as from $16\%$ to $7\%$ in the case of early integration. \ja{Why does this happen?}
This is in accordance with previous results on similarity retrieval, as well as comparisons between mel-frequency coefficients and scattering coefficients for tasks ranging from musical genre recognition and phone segment classification \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

>>>>

As shown in Figure \ref{fig:folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
This is in accordance with previous results on similarity retrieval, as well as comparisons between mel-frequency coefficients and scattering coefficients for tasks ranging from musical genre recognition and phone segment classification \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.
